Supplimentary materials

### 2020-08-14 supplimentary/supplimentary_tables.tex
pre figure removeal

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Supplimentary materials},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{float}
\usepackage{longtable}
\pagenumbering{gobble}
\usepackage{caption}
\captionsetup[table]{labelformat=empty}
% https://github.com/rstudio/rmarkdown/issues/337
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

% https://github.com/rstudio/rmarkdown/pull/252
\usepackage{titling}
\setlength{\droptitle}{-2em}

\pretitle{\vspace{\droptitle}\centering\huge}
\posttitle{\par}

\preauthor{\centering\large\emph}
\postauthor{\par}

\predate{\centering\large\emph}
\postdate{\par}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\title{Supplimentary materials}
\date{}

@@

\begin{longtable}[t]{l|l|r|r}
\caption{\label{tab:unnamed-chunk-3}}\\
\hline
from & to & strength & direction\\
\hline
\endfirsthead
\caption[]{ S3 Table continued}\\
\hline
from & to & strength & direction\\
\hline
\endhead
nlebase & nlelg\_1 & 1.00 & 1.00\\
\hline
nlebase & nlelg\_2 & 1.00 & 1.00\\
\hline
nlelg\_1 & injured\_1 & 1.00 & 1.00\\
\hline
nlelg\_2 & injured\_2 & 1.00 & 1.00\\
\hline
BIS\_1 & FFFS\_1 & 0.98 & 0.68\\
\hline
FFFS\_1 & BIS\_1 & 0.98 & 0.32\\
\hline
ind\_team & hours & 0.95 & 0.50\\
\hline
hours & ind\_team & 0.95 & 0.50\\
\hline
nlebase & RI\_1 & 0.83 & 1.00\\
\hline
ind\_team & nlebase & 0.78 & 1.00\\
\hline
BIS\_2 & FFFS\_2 & 0.73 & 0.71\\
\hline
FFFS\_2 & BIS\_2 & 0.73 & 0.29\\
\hline
gender & stiffness\_1 & 0.72 & 1.00\\
\hline
hours & rmssd\_1 & 0.66 & 1.00\\
\hline
gender & stiffness\_2 & 0.60 & 1.00\\
\hline
nlelg\_1 & BIS\_1 & 0.52 & 0.97\\
\hline
BIS\_1 & nlelg\_1 & 0.52 & 0.03\\
\hline
pi & stiffness\_1 & 0.51 & 1.00\\
\hline
injured\_2 & stiffness\_2 & 0.51 & 0.65\\
\hline
stiffness\_2 & injured\_2 & 0.51 & 0.35\\
\hline
clevel & balance\_1 & 0.49 & 1.00\\
\hline
FFFS\_1 & BIS\_2 & 0.49 & 1.00\\
\hline
nlebase & rmssd\_1 & 0.49 & 1.00\\
\hline
injured\_1 & stiffness\_1 & 0.46 & 0.34\\
\hline
stiffness\_1 & injured\_1 & 0.46 & 0.66\\
\hline
clevel & RI\_2 & 0.46 & 1.00\\
\hline
FFFS\_1 & injured\_2 & 0.44 & 1.00\\
\hline
hours & injured\_1 & 0.40 & 1.00\\
\hline
nlelg\_2 & BIS\_2 & 0.38 & 0.98\\
\hline
BIS\_2 & nlelg\_2 & 0.38 & 0.02\\
\hline
gender & FFFS\_1 & 0.37 & 1.00\\
\hline
injured\_2 & rmssd\_2 & 0.37 & 0.84\\
\hline
rmssd\_2 & injured\_2 & 0.37 & 0.16\\
\hline
pi & nlelg\_2 & 0.37 & 1.00\\
\hline
nlebase & RI\_2 & 0.36 & 1.00\\
\hline
RI\_1 & BIS\_1 & 0.34 & 0.44\\
\hline
BIS\_1 & RI\_1 & 0.34 & 0.56\\
\hline
injured\_2 & balance\_2 & 0.34 & 0.95\\
\hline
balance\_2 & injured\_2 & 0.34 & 0.05\\
\hline
injured\_1 & balance\_1 & 0.34 & 0.68\\
\hline
balance\_1 & injured\_1 & 0.34 & 0.32\\
\hline
gender & FFFS\_2 & 0.33 & 1.00\\
\hline
RI\_1 & balance\_1 & 0.32 & 0.21\\
\hline
balance\_1 & RI\_1 & 0.32 & 0.79\\
\hline
pi & clevel & 0.32 & 0.50\\
\hline
clevel & pi & 0.32 & 0.50\\
\hline
BIS\_1 & FFFS\_2 & 0.32 & 1.00\\
\hline
pi & ind\_team & 0.31 & 0.44\\
\hline
ind\_team & pi & 0.31 & 0.56\\
\hline
pi & stiffness\_2 & 0.31 & 1.00\\
\hline
ind\_team & FFFS\_1 & 0.30 & 1.00\\
\hline
\end{longtable}

@@

\begin{longtable}[t]{l|l|r|r}
\caption{\label{tab:unnamed-chunk-4}}\\
\hline
from & to & strength & direction\\
\hline
BIS & FFFS & 1.00 & 0.75\\
\hline
FFFS & BIS & 1.00 & 0.25\\
\hline
hours & injured & 0.72 & 1.00\\
\hline
injured & stiffness & 0.66 & 1.00\\
\hline
rmssd & FFFS & 0.64 & 0.67\\
\hline
FFFS & rmssd & 0.64 & 0.33\\
\hline
clevel & BIS & 0.61 & 1.00\\
\hline
gender & stiffness & 0.57 & 1.00\\
\hline
injured & nlec & 0.45 & 1.00\\
\hline
pi & balance & 0.42 & 1.00\\
\hline
pi & injured & 0.38 & 1.00\\
\hline
RI & BIS & 0.36 & 0.35\\
\hline
BIS & RI & 0.36 & 0.65\\
\hline
stiffness & BIS & 0.34 & 0.92\\
\hline
BIS & stiffness & 0.34 & 0.08\\
\hline
\end{longtable}

@@

\caption{\label{tab:unnamed-chunk-5}}
\centering
\begin{tabular}[t]{l|l|l|l|l|l}
\hline
prob & clevel & hours & nlelg\_1 & stiffness\_1 & balance\_1\\
\hline
0.53 & club\_university\_county & High & Low & High & High\\
\hline
0.46 & national\_international & High & Low & High & Low\\
\hline
0.44 & national\_international & High & Low & High & High\\
\hline
0.39 & club\_university\_county & Low & High & High & High\\
\hline
0.37 & club\_university\_county & High & Low & High & Low\\
\hline
0.34 & club\_university\_county & High & High & High & High\\
\hline
0.32 & national\_international & Low & High & High & Low\\
\hline
0.3 & national\_international & Low & High & High & High\\
\hline
0.29 & club\_university\_county & Low & High & Low & High\\
\hline
0.29 & club\_university\_county & High & High & Low & High\\
\hline
0.27 & national\_international & High & High & High & Low\\
\hline
0.26 & national\_international & High & High & High & High\\
\hline
0.25 & club\_university\_county & Low & High & High & Low\\
\hline
0.24 & national\_international & Low & High & Low & Low\\
\hline
0.23 & national\_international & High & High & Low & Low\\
\hline
0.22 & national\_international & Low & High & Low & High\\
\hline
0.22 & national\_international & High & High & Low & High\\
\hline
0.21 & club\_university\_county & High & High & High & Low\\
\hline
0.18 & club\_university\_county & Low & High & Low & Low\\
\hline
0.18 & club\_university\_county & High & High & Low & Low\\
\hline
0.17 & club\_university\_county & Low & Low & High & High\\
\hline
0.16 & club\_university\_county & High & Low & Low & High\\
\hline
0.13 & national\_international & Low & Low & High & Low\\
\hline
0.12 & national\_international & High & Low & Low & Low\\
\hline
0.12 & national\_international & Low & Low & High & High\\
\hline
0.12 & national\_international & High & Low & Low & High\\
\hline
0.09 & club\_university\_county & Low & Low & High & Low\\
\hline
0.09 & club\_university\_county & High & Low & Low & Low\\
\hline
0.07 & club\_university\_county & Low & Low & Low & High\\
\hline
0.06 & national\_international & Low & Low & Low & Low\\
\hline
0.05 & national\_international & Low & Low & Low & High\\
\hline
0.04 & club\_university\_county & Low & Low & Low & Low\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-6}}
\centering
\begin{tabular}[t]{r|l|l|l|l|l}
\hline
prob & FFFS\_1 & nlelg\_2 & stiffness\_2 & rmssd\_2 & balance\_2\\
\hline
0.53 & Low & Low & High & Low & High\\
\hline
0.45 & Low & High & High & Low & High\\
\hline
0.41 & Low & Low & High & High & High\\
\hline
0.39 & Low & Low & High & Low & Low\\
\hline
0.34 & Low & High & High & High & High\\
\hline
0.32 & Low & High & High & Low & Low\\
\hline
0.31 & Low & Low & Low & Low & High\\
\hline
0.29 & Low & Low & High & High & Low\\
\hline
0.28 & Low & High & Low & Low & High\\
\hline
0.25 & High & Low & High & Low & High\\
\hline
0.23 & Low & High & High & High & Low\\
\hline
0.22 & Low & Low & Low & High & High\\
\hline
0.21 & High & High & High & Low & High\\
\hline
0.21 & Low & Low & Low & Low & Low\\
\hline
0.19 & Low & High & Low & High & High\\
\hline
0.18 & Low & High & Low & Low & Low\\
\hline
0.17 & High & Low & High & High & High\\
\hline
0.16 & High & Low & High & Low & Low\\
\hline
0.14 & High & High & High & High & High\\
\hline
0.14 & Low & Low & Low & High & Low\\
\hline
0.13 & High & High & High & Low & Low\\
\hline
0.13 & High & Low & Low & Low & High\\
\hline
0.12 & Low & High & Low & High & Low\\
\hline
0.12 & High & High & Low & Low & High\\
\hline
0.11 & High & Low & High & High & Low\\
\hline
0.08 & High & High & High & High & Low\\
\hline
0.08 & High & Low & Low & High & High\\
\hline
0.08 & High & Low & Low & Low & Low\\
\hline
0.07 & High & High & Low & High & High\\
\hline
0.07 & High & High & Low & Low & Low\\
\hline
0.05 & High & Low & Low & High & Low\\
\hline
0.04 & High & High & Low & High & Low\\
\hline
\end{tabular}
\end{table}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Supplimentary materials},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{float}
\usepackage{longtable}
\pagenumbering{gobble}
\usepackage{caption}
\captionsetup[table]{labelformat=empty}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\title{Supplimentary materials}
\author{}
\date{\vspace{-2.5em}}

@@

\begin{longtable}[t]{l|l|r|r}
\caption{\label{tab:unnamed-chunk-3}}\\
\hline
from & to & strength & direction\\
\hline
\endfirsthead
\caption[]{ S2 Table continued}\\
\hline
from & to & strength & direction\\
\hline
\endhead
nlebase & nlelg\_1 & 1.00 & 1.00\\
\hline
nlebase & nlelg\_2 & 1.00 & 1.00\\
\hline
nlelg\_1 & injured\_1 & 1.00 & 1.00\\
\hline
nlelg\_2 & injured\_2 & 1.00 & 1.00\\
\hline
BIS\_1 & FFFS\_1 & 0.98 & 0.70\\
\hline
FFFS\_1 & BIS\_1 & 0.98 & 0.30\\
\hline
ind\_team & hours & 0.94 & 0.50\\
\hline
hours & ind\_team & 0.94 & 0.50\\
\hline
nlebase & RI\_1 & 0.84 & 1.00\\
\hline
ind\_team & nlebase & 0.78 & 1.00\\
\hline
BIS\_2 & FFFS\_2 & 0.74 & 0.71\\
\hline
FFFS\_2 & BIS\_2 & 0.74 & 0.29\\
\hline
gender & stiffness\_1 & 0.71 & 1.00\\
\hline
pi & stiffness\_1 & 0.57 & 1.00\\
\hline
nlelg\_1 & BIS\_1 & 0.55 & 0.97\\
\hline
BIS\_1 & nlelg\_1 & 0.55 & 0.03\\
\hline
FFFS\_1 & BIS\_2 & 0.52 & 1.00\\
\hline
clevel & balance\_1 & 0.47 & 1.00\\
\hline
injured\_2 & stiffness\_2 & 0.46 & 0.66\\
\hline
stiffness\_2 & injured\_2 & 0.46 & 0.34\\
\hline
injured\_1 & stiffness\_1 & 0.46 & 0.36\\
\hline
stiffness\_1 & injured\_1 & 0.46 & 0.64\\
\hline
gender & stiffness\_2 & 0.43 & 1.00\\
\hline
FFFS\_1 & injured\_2 & 0.42 & 1.00\\
\hline
hours & injured\_1 & 0.42 & 1.00\\
\hline
clevel & RI\_2 & 0.42 & 1.00\\
\hline
nlebase & hrv\_1 & 0.41 & 1.00\\
\hline
hours & hrv\_1 & 0.40 & 1.00\\
\hline
hrv\_1 & nlelg\_2 & 0.39 & 1.00\\
\hline
gender & FFFS\_1 & 0.37 & 1.00\\
\hline
injured\_2 & hrv\_2 & 0.37 & 0.89\\
\hline
nlelg\_2 & BIS\_2 & 0.37 & 0.96\\
\hline
BIS\_2 & nlelg\_2 & 0.37 & 0.04\\
\hline
hrv\_2 & injured\_2 & 0.37 & 0.11\\
\hline
pi & nlelg\_2 & 0.36 & 1.00\\
\hline
RI\_1 & BIS\_1 & 0.36 & 0.41\\
\hline
BIS\_1 & RI\_1 & 0.36 & 0.59\\
\hline
nlebase & RI\_2 & 0.36 & 1.00\\
\hline
injured\_1 & balance\_1 & 0.36 & 0.70\\
\hline
balance\_1 & injured\_1 & 0.36 & 0.30\\
\hline
injured\_2 & balance\_2 & 0.34 & 0.94\\
\hline
balance\_2 & injured\_2 & 0.34 & 0.06\\
\hline
RI\_1 & balance\_1 & 0.33 & 0.22\\
\hline
balance\_1 & RI\_1 & 0.33 & 0.78\\
\hline
gender & FFFS\_2 & 0.33 & 1.00\\
\hline
pi & clevel & 0.32 & 0.50\\
\hline
clevel & pi & 0.32 & 0.50\\
\hline
ind\_team & FFFS\_1 & 0.31 & 1.00\\
\hline
BIS\_1 & FFFS\_2 & 0.31 & 1.00\\
\hline
pi & ind\_team & 0.30 & 0.46\\
\hline
ind\_team & pi & 0.30 & 0.54\\
\hline
\end{longtable}

\clearpage
\newpage

@@

\begin{longtable}[t]{l|l|r|r}
\caption{\label{tab:unnamed-chunk-4}}\\
\hline
from & to & strength & direction\\
\hline
BIS & FFFS & 1.00 & 0.76\\
\hline
FFFS & BIS & 1.00 & 0.25\\
\hline
hours & injured & 0.72 & 1.00\\
\hline
injured & stiffness & 0.67 & 1.00\\
\hline
clevel & BIS & 0.60 & 1.00\\
\hline
hrv & FFFS & 0.58 & 0.69\\
\hline
FFFS & hrv & 0.58 & 0.31\\
\hline
gender & stiffness & 0.56 & 1.00\\
\hline
injured & nlec & 0.45 & 1.00\\
\hline
pi & balance & 0.43 & 1.00\\
\hline
pi & injured & 0.38 & 1.00\\
\hline
stiffness & BIS & 0.38 & 0.93\\
\hline
BIS & stiffness & 0.38 & 0.07\\
\hline
RI & BIS & 0.35 & 0.29\\
\hline
BIS & RI & 0.35 & 0.71\\
\hline
pi & hrv & 0.33 & 1.00\\
\hline
\end{longtable}

@@

\caption{\label{tab:unnamed-chunk-5}}
\centering
\begin{tabular}[t]{l|l|l|l|l|l}
\hline
prob & clevel & hours & nlelg\_1 & stiffness\_1 & balance\_1\\
\hline
0.53 & club\_university\_county & High & Low & High & High\\
\hline
0.46 & national\_international & High & Low & High & Low\\
\hline
0.44 & national\_international & High & Low & High & High\\
\hline
0.39 & club\_university\_county & Low & High & High & High\\
\hline
0.37 & club\_university\_county & High & Low & High & Low\\
\hline
0.32 & national\_international & Low & High & High & Low\\
\hline
0.32 & club\_university\_county & High & High & High & High\\
\hline
0.31 & club\_university\_county & High & High & Low & High\\
\hline
0.3 & national\_international & Low & High & High & High\\
\hline
0.29 & club\_university\_county & Low & High & Low & High\\
\hline
0.25 & national\_international & High & High & High & Low\\
\hline
0.25 & national\_international & High & High & Low & Low\\
\hline
0.25 & club\_university\_county & Low & High & High & Low\\
\hline
0.24 & national\_international & High & High & Low & High\\
\hline
0.24 & national\_international & High & High & High & High\\
\hline
0.24 & national\_international & Low & High & Low & Low\\
\hline
0.22 & national\_international & Low & High & Low & High\\
\hline
0.19 & club\_university\_county & High & High & Low & Low\\
\hline
0.19 & club\_university\_county & High & High & High & Low\\
\hline
0.18 & club\_university\_county & Low & High & Low & Low\\
\hline
0.17 & club\_university\_county & Low & Low & High & High\\
\hline
0.16 & club\_university\_county & High & Low & Low & High\\
\hline
0.13 & national\_international & Low & Low & High & Low\\
\hline
0.12 & national\_international & High & Low & Low & Low\\
\hline
0.12 & national\_international & Low & Low & High & High\\
\hline
0.12 & national\_international & High & Low & Low & High\\
\hline
0.09 & club\_university\_county & Low & Low & High & Low\\
\hline
0.09 & club\_university\_county & High & Low & Low & Low\\
\hline
0.07 & club\_university\_county & Low & Low & Low & High\\
\hline
0.06 & national\_international & Low & Low & Low & Low\\
\hline
0.05 & national\_international & Low & Low & Low & High\\
\hline
0.04 & club\_university\_county & Low & Low & Low & Low\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-6}}
\centering
\begin{tabular}[t]{r|l|l|l|l|l}
\hline
prob & FFFS\_1 & nlelg\_2 & stiffness\_2 & hrv\_2 & balance\_2\\
\hline
0.53 & Low & Low & High & Low & High\\
\hline
0.46 & Low & High & High & Low & High\\
\hline
0.41 & Low & Low & High & High & High\\
\hline
0.39 & Low & Low & High & Low & Low\\
\hline
0.35 & Low & High & High & High & High\\
\hline
0.33 & Low & High & High & Low & Low\\
\hline
0.32 & Low & Low & Low & Low & High\\
\hline
0.28 & Low & Low & High & High & Low\\
\hline
0.26 & Low & High & Low & Low & High\\
\hline
0.25 & High & Low & High & Low & High\\
\hline
0.23 & Low & High & High & High & Low\\
\hline
0.23 & Low & Low & Low & High & High\\
\hline
0.22 & High & High & High & Low & High\\
\hline
0.21 & Low & Low & Low & Low & Low\\
\hline
0.18 & Low & High & Low & High & High\\
\hline
0.17 & High & Low & High & High & High\\
\hline
0.17 & Low & High & Low & Low & Low\\
\hline
0.16 & High & Low & High & Low & Low\\
\hline
0.15 & High & High & High & High & High\\
\hline
0.14 & Low & Low & Low & High & Low\\
\hline
0.13 & High & High & High & Low & Low\\
\hline
0.13 & High & Low & Low & Low & High\\
\hline
0.11 & Low & High & Low & High & Low\\
\hline
0.11 & High & High & Low & Low & High\\
\hline
0.11 & High & Low & High & High & Low\\
\hline
0.09 & High & High & High & High & Low\\
\hline
0.08 & High & Low & Low & High & High\\
\hline
0.08 & High & Low & Low & Low & Low\\
\hline
0.07 & High & High & Low & High & High\\
\hline
0.06 & High & High & Low & Low & Low\\
\hline
0.05 & High & Low & Low & High & Low\\
\hline
0.04 & High & High & Low & High & Low\\
\hline
\end{tabular}
\end{table}

\textbf{S6 Table. Highest and lowest probability of injury, conditional on the all variables in the Markov blanket for ``injured''.}

\begin{table}[H]
\centering
\begin{tabular}{c|c|c|c|c}
\hline
\textbf{Probability} & \textbf{hours} & \textbf{pi} & \textbf{nle} & \textbf{stiffness}\\
\hline
0.77 & High & injury & +1SD & +1SD\\
\hline
0.74 & High & no injury & +1SD & +1SD\\
\hline
0.72 & Low & injury & +1SD & +1SD\\
\hline
0.70 & High & injury & +1SD & mean\\
\hline
0.69 & High & injury & +1SD & -1SD\\
\hline
0.68 & High & no injury & +1SD & mean\\
\hline
0.66 & High & no injury & +1SD & -1SD\\
\hline
0.65 & Low & injury & +1SD & mean\\
\hline
0.64 & Low & injury & +1SD & -1SD\\
\hline
0.61 & High & injury & mean & +1SD\\
\hline
0.58 & High & no injury & mean & +1SD\\
\hline
0.54 & Low & injury & mean & +1SD\\
\hline
0.54 & High & injury & mean & mean\\
\hline
0.51 & High & injury & -1SD & +1SD\\
\hline
0.51 & High & injury & mean & -1SD\\
\hline
0.50 & High & no injury & mean & mean\\
\hline
0.48 & High & no injury & mean & -1SD\\
\hline
0.48 & Low & injury & mean & mean\\
\hline
0.47 & High & no injury & -1SD & +1SD\\
\hline
0.46 & Low & injury & mean & -1SD\\
\hline
0.44 & Low & injury & -1SD & +1SD\\
\hline
0.44 & High & injury & -1SD & mean\\
\hline
0.42 & High & injury & -1SD & -1SD\\
\hline
0.41 & High & no injury & -1SD & mean\\
\hline
0.38 & High & no injury & -1SD & -1SD\\
\hline
0.37 & Low & no injury & +1SD & +1SD\\
\hline
0.37 & Low & injury & -1SD & mean\\
\hline
0.35 & Low & injury & -1SD & -1SD\\
\hline
0.32 & Low & no injury & +1SD & mean\\
\hline
0.29 & Low & no injury & +1SD & -1SD\\
\hline
0.20 & Low & no injury & mean & +1SD\\
\hline
0.18 & Low & no injury & mean & mean\\
\hline
0.16 & Low & no injury & mean & -1SD\\
\hline
0.15 & Low & no injury & -1SD & +1SD\\
\hline
0.13 & Low & no injury & -1SD & mean\\
\hline
0.11 & Low & no injury & -1SD & -1SD\\
\hline
\end{tabular}
\end{table}

### 2020-08-14 supplimentary_tables.Rmd
pre figure removeal

```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
pacman::p_load(tidyverse, knitr, kableExtra, qwraps2, brms, broom.mixed, bnlearn)

@@

@@

tab4 <- newprobtable(
  tallc,
  c("balance_2", "stiffness_2", "nlelg_2", "FFFS_1", "rmssd_2"),
  "injured_2",
  "injured",
  avg30
) %>%
  arrange(-prob) %>%
  select(outcome, everything()) %>%
  dendroTools::round_df(2) %>%
  select(7, 2:6) %>%
  `colnames<-`(str_replace_all(colnames(.), "_", "\\\\_"))

@@

>>>>

```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
pacman::p_load(tidyverse, knitr, kableExtra, qwraps2, brms, broom.mixed, bnlearn)

@@

\clearpage
\newpage

@@

tab4 <- newprobtable(
  tallc,
  c("balance_2", "stiffness_2", "nlelg_2", "FFFS_1", "hrv_2"),
  "injured_2",
  "injured",
  avg30
) %>%
  arrange(-prob) %>%
  select(outcome, everything()) %>%
  dendroTools::round_df(2) %>%
  select(7, 2:6) %>%
  `colnames<-`(str_replace_all(colnames(.), "_", "\\\\_"))

@@

\textbf{S6 Table. Highest and lowest probability of injury, conditional on the all variables in the Markov blanket for ``injured''.}

```{r results='asis'}
set.seed(1007)
testt <- expand.grid(list(
  c(-1:1),
  c(-1:1),
  c("Low", "High"),
  c("injury", "no injury")
))

query7 <- pmap_dfr(
  .l = testt,
  ~ tibble(
    prob = cpquery(
      fittedcont,
      event = (injured == "injured"),
      evidence = list(
        nlec = as.numeric(..1),
        stiffness = as.numeric(..2),
        hours = ..3,
        pi = ..4
      ),
      method = "lw"
    ),
    nle = ..1,
    stiffness = ..2,
    hours = ..3,
    pi = ..4
  )
) %>%
  arrange(-prob)

query7 %>%
  mutate_at(vars(nle, stiffness), ~ case_when(
    . == 1 ~ "+1SD",
    . == 0 ~ "mean",
    . == -1 ~ "-1SD"
  )) %>%
  select(prob, hours, pi, nle, stiffness) %>%
  rename(Probability = "prob") %>%
  dendroTools::round_df(2) %>%
  kable(
    .,
    align = "ccccc"
  ) %>%
  kable_styling(latex_options = "HOLD_position") %>%

  row_spec(0,bold=TRUE)
```
